### 2024-05-21 README.Rmd
fix md issue

<!-- badges: start -->
[![R-CMD-check](https://github.com/idem-lab/traveltime/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/idem-lab/traveltime/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/idem-lab/traveltime/branch/main/graph/badge.svg)](https://app.codecov.io/gh/idem-lab/traveltime?branch=main)
![GitHub License](https://img.shields.io/github/license/geryan/traveltime)
[![Lifecycle:](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
![GitHub commit activity](https://img.shields.io/github/commit-activity/w/geryan/traveltime)
![GitHub Downloads (all assets, all releases)](https://img.shields.io/github/downloads/geryan/traveltime/total)
![GitHub last commit](https://img.shields.io/github/last-commit/geryan/traveltime)
![GitHub commits since latest release](https://img.shields.io/github/commits-since/geryan/traveltime/latest)
<!-- badges: end -->

>>>>

<!-- badges: start -->
[![traveltime status badge](https://idem-lab.r-universe.dev/badges/traveltime)](https://idem-lab.r-universe.dev/traveltime)
[![R-CMD-check](https://github.com/idem-lab/traveltime/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/idem-lab/traveltime/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/idem-lab/traveltime/branch/main/graph/badge.svg)](https://app.codecov.io/gh/idem-lab/traveltime?branch=main)
![GitHub License](https://img.shields.io/github/license/geryan/traveltime)
[![Lifecycle:](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
![GitHub commit activity](https://img.shields.io/github/commit-activity/w/geryan/traveltime)
![GitHub Downloads (all assets, all releases)](https://img.shields.io/github/downloads/geryan/traveltime/total)
![GitHub last commit](https://img.shields.io/github/last-commit/geryan/traveltime)
![GitHub commits since latest release](https://img.shields.io/github/commits-since/geryan/traveltime/latest)
<!-- badges: end -->
